Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-20 outputs/paper/paper.qmd
updates to paper written content

In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper]. Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper]. Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence [@main_paper.

Our paper will follow a reproduction of Dancygier, Egami, Jamal, and Rischke's findings and apply a Canadian-facing lens to discuss its implications on local Canadian populations and increased anti-refugee/ immigrant sentiments and violence. Our paper seeks to address the two following research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians. Our reproduction was conducted using the statistical programming language R [@citeR]. To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich [sandwich], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr], kableExtra [@kableExtra.

@@

-   Hostility against refugees justified

@@

-   Refugee integration in Germany

@@

## Implications

>>>>

In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper]. This population of individuals, non-immigrant German males in highly male populated municipalities being the estimand of the study. Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper]. Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence \[@main_paper.

Our paper will follow a reproduction of Dancygier, Egami, Jamal, and Rischke's findings and apply a Canadian-facing lens to discuss its implications on local Canadian populations and increased anti-refugee/ immigrant sentiments and violence. Our paper seeks to address the two following research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians. Our reproduction was conducted using the statistical programming language R [@citeR]. To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich \[sandwich\], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr], kableExtra \[@kableExtra.

@@

-   Hostility against refugees is justified

@@

-   Refugees are integrating well into Germany

@@
